A new tidy data structure to support exploration and modeling of temporal data

### 2019-01-19 main.Rmd
done with 5.4

As a fundamental infrastructure, extensibility is a design decision that is focused on from the start of **tsibble**'s development. Contrary to the "data first" principle for end users, extensibility is developer focused and would be mostly used in dependent packages, which heavily relies on S3 classes and methods in R [@adv-r]. It can be extended in two major aspects: custom index and new tsibble class.

Time representation could be arbitrary, for example R's native `POSIXct` and `Date` for versatile date-times, nano time for nanosecond resolution implemented in **nantotime** [@R-nanotime], and pure numbers in simulations. Yet ordered factors can also be a source of time, such as month names from January to December and weekdays from Monday to Sunday. Tsibble supports an extensive range of index types from numerics to nano time, but there might be custom indexes used for some occasions, for example school semesters. These academic terms vary from one institute to another within an academic year, which is defined differently from a calendar year. New index would be immediately recognized by the software upon defining `index_valid()`, as long as it can be ordered from past to future. The interval regarding semesters is further outlined through `pull_interval()`. As a result, the rest software methods such as `has_gaps()`, `count_gaps()` and `fill_gaps()` will have instant support for data that contains this new index.

The class of tsibble is an underlying basis of temporal data, and there is a demand for sub-classing a tsibble. For example, a fable is actually an extension to a tsibble, mentioned in Section \ref{sec:timepipeline}. A low-level constructor `new_tsibble()` provides a vehicle to easily create a new subclass. First of all, this new object itself is a tsibble. It perhaps needs more metadata than those of a tsibble, that gives rise to a new data extension, like prediction distributions to a fable. Tsibble verbs are also S3 generics. Developers will be able to implement these verbs for the new class if needed.

>>>>

As a fundamental infrastructure, extensibility is a design decision that was employed from the start of **tsibble**'s development. Contrary to the "data first" principle for end users, extensibility is developer focused and would be mostly used in dependent packages, which heavily rely on S3 classes and methods in R [@adv-r]. The package can be extended in two major aspects: custom index and new tsibble class.

Time representation could be arbitrary, for example R's native `POSIXct` and `Date` for versatile date-times, nano time for nanosecond resolution implemented in **nantotime** [@R-nanotime], and pure numbers in simulations. Ordered factors can also be a source of time, such as month names, January to December, and weekdays, Monday to Sunday. The tsibble package supports an extensive range of index types from numerics to nano time, but there might be custom indexes used for some occasions, for example school semesters. These academic terms vary from one institution to another, within an academic year which is defined differently from a calendar year. New index would be immediately recognized by the software upon defining `index_valid()`, as long as it can be ordered from past to future. The interval regarding semesters is further outlined through `pull_interval()`. As a result, the rest of the software methods such as `has_gaps()`, `count_gaps()` and `fill_gaps()` will have instant support for data that contains this new index.

The class of tsibble is an underlying basis of temporal data, and there is a demand for sub-classing a tsibble. For example, a mable is actually an extension of a tsibble, mentioned in Section \ref{sec:timepipeline}. A low-level constructor `new_tsibble()` provides a vehicle to easily create a new subclass. This new object itself is a tsibble. It perhaps needs more metadata than those of a tsibble, that gives rise to a new data extension, like prediction distributions to a mable. Tsibble verbs are also S3 generics. Developers will be able to implement these verbs for the new class if needed.
